No meaningful effects of COVID-19 related social media use on well-being

### 2021-11-09 index.Rmd
- corrected typo on landing page.

---
title: "No effets of COVID-related social media use and well-being"
---

On this website, you can find the companion material for the paper _No effets of COVID-related social media use and well-being_.

>>>>

---
title: "No meaningful effects of COVID-19 related social media use on well-being"
---

On this website, you can find the companion material for the paper _No meaningful effects of COVID-19 related social media use on well-being_.
